Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-18 paper-1/manuscript.tex
Disambiguate T (TA) from T (stats)
Minor tweak for script compat

% Common notation
\renewcommand{\R}[3][]{{}^{#1}_{}\!R^{#2}_{#3}}
\renewcommand{\T}[3][]{{}^{#1}_{}T^{#2}_{#3}}
\newcommand{\D}[3][]{{}^{#1}_{}\!D^{#2}_{#3}}
\newcommand{\mean}[1]{\overline{#1}}

@@

@@

\begin{figure*}%
    \centering
    \includegraphics{sfig-STD-correlation-decay.pdf}
    \caption{}
    \label{sfig-STD-correlation-decay}
\end{figure*}
\textbf{Figure S?} The STD variable $x_i$ only correlates with the activity of the immediately preceding trial. Each marker represents the coefficient $\rho$ of the Pearson correlation between the spike counts in a target trial and the corresponding values $x_i$ at the beginning of the immediately following trial ($\Delta$ trials = 1) or after one intervening trial ($\Delta$ trials = 2). Recall that $x$ is reduced upon spiking, which implies that an effective correlation is negative. Color represents the p-value of the alternative hypothesis that $\rho < 0$. Horizontal lines indicate the median $\rho$ and p. Horizontal jitter is introduced to aid visual separability of the markers.

>>>>

% Common notation
\renewcommand{\R}[3][]{{}^{#1}_{}\!\mathbf{R}^{#2}_{#3}}
\renewcommand{\T}[3][]{{}^{#1}_{}\mathbf{T}^{#2}_{#3}}
\newcommand{\D}[3][]{{}^{#1}_{}\!\mathbf{D}^{#2}_{#3}}
\newcommand{\mean}[1]{\overline{#1}}

@@

For disambiguation, note that the quantity $\T{X}{i}$, regardless of sub- and superscripts, is always in bold math font, whereas the Wilcoxon statistic T is typeset in normal font.

@@

\begin{figure*}%
    \centering
    \includegraphics{sfig-STD-correlation-decay.pdf}
    \caption{}
    \label{sfig-STD-correlation-decay}
\end{figure*}
\textbf{Fig. S?} The STD variable $x_i$ only correlates with the activity of the immediately preceding trial. Each marker represents the coefficient $\rho$ of the Pearson correlation between the spike counts in a target trial and the corresponding values $x_i$ at the beginning of the immediately following trial ($\Delta$ trials = 1) or after one intervening trial ($\Delta$ trials = 2). Recall that $x$ is reduced upon spiking, which implies that an effective correlation is negative. Color represents the p-value of the alternative hypothesis that $\rho < 0$. Horizontal lines indicate the median $\rho$ and p. Horizontal jitter is introduced to aid visual separability of the markers.
